### 2016-03-27 chapters/background.tex
TODOs added
contributions fixed, workflow image added, citation added

During configuration a user selects or deselects features to his needs. This process requires a lot of domain knowledge on the one hand and detailed information about the implementation of each single feature on the other. With growing numbers of features and thus growing numbers of possible products configuration requires more effort. However, the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration. The overhead of configuration might even outright negate the benefit gained from using a product line instead of multiple stand-alone products. This trade-off has to be considered or addressed through modification of the configuration process.

{\color{red}TODO: introduce partial configuration}

\subsection{Satisfiability}
A feature model can be expressed as a propositional statement. The mapping between the individual groups (sub-trees) and the corresponding propositional expression is shown in the following list:

>>>>

During configuration a user selects or deselects features to his needs. This process requires a lot of domain knowledge on the one hand and detailed information about the implementation of each single feature on the other. With growing numbers of features and thus growing numbers of possible products configuration requires more effort. However, the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration. The automatic selection or deselection of a features doe to propagation of a made selection always results in a valid configuration. Nevertheless the propagated selections can be confusing for the user.

A non-final configuration, that is a configuration that still has some feature choices left to be made, is called a \textit{partial configuration}. A \textit{valid} partial configuration can be useful, as it narrows down the number of possible resulting variations and choices left to make.

\subsection{Satisfiability}
%TODO: rausschmeißen?
A feature model can be expressed as a propositional statement. The mapping between the individual groups (sub-trees) and the corresponding propositional expression is shown in the following list:

### 2016-03-27 chapters/intro.tex
TODOs added
contributions fixed, workflow image added, citation added

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
Developing feature oriented, although bringing with it some overhead, facilitates the creation of software when it is planned on custom tailoring it for a multiple number of clients. Feature oriented means developing and maintaining single features that can be combined with others to create a whole product. All of the individual features make up a product line, whereas a subset of those features create a variant of this product. Developing software product lines can result in a large amount of variants, when customizing the software to each customers needs. By developing with a feature-oriented approach the configuration of a single variant can be done by selecting the features a customer needs, automatically including its dependencies. The configuration is based on a Feature Model, that defines the available Features and its relations to one another.

% TODO: fosd buch zitieren, FM Zitat
Feature Models are essential structures for the feature-oriented development and later configuration of software product lines (SPL). They give a complete and understandable overview of the given features and constraints of a product-line. There are projects being developed in a feature-oriented manner, but don't have a feature model yet. Implementing it on top of a given Project can result in a complex task due to the amount of its features and the constraints between them. Nevertheless the benefits of a correct feature model justify the effort to extract one out of a live project. This work aims at automatically generating it out of descriptive files and naming conventions, to simplify a big part of the feature model creation.

@@

FeatureIDE is an open source IDE for feature-oriented-software development. It provides all the functionality needed to programmatically generate and work with feature models.
% TODO: was benutzt ihr denn genau?
 The underlying Eclipse enables us to implement the feature extraction and the questionnaire as a plugin.

@@

Contributions:
\begin{itemize}
\item Automatic feature model generation based on descriptive files and naming conventions
\item Eclipse plugin, that enables the creation of a questionnaire based on a configuration file and the associated feature model
\item The questionnaire changes as choices are made based on the logic behind the configuration file and the dependencies of the feature model
\item Exiting the questionnaire always results in a valid configured variant 
\end{itemize}

>>>>

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
Developing feature oriented, although bringing with it some overhead, facilitates the creation of software when it is planned on custom tailoring it for a multiple number of clients. Feature oriented means developing and maintaining single features that can be combined with others to create a whole product. All of the individual features make up a product line, whereas a subset of those features create a variant of this product. Developing software product lines can result in a large amount of variants, when customizing the software to each customers needs. By developing with a feature-oriented approach the configuration of a single variant can be done by selecting the features a customer needs, automatically including its dependencies. The configuration is based on a Feature Model, that defines the available Features and its relations to one another. A feature model documents the features of a product line and their relationships\cite{fospl}.

Feature Models are essential structures for the feature-oriented development and later configuration of software product lines (SPL). There are projects being developed in a feature-oriented manner, but don't have a feature model yet. Implementing it on top of a given Project can result in a complex task due to the amount of its features and the constraints between them. Nevertheless the benefits of a correct feature model justify the effort to extract one out of a live project. This work aims at automatically generating it out of descriptive files and naming conventions, to simplify a big part of the feature model creation.

@@

FeatureIDE is an open source IDE for feature-oriented-software development. It provides all the functionality needed to programmatically generate and work with feature models. This includes the logic behind configurations, data structures and the visualization and processing of feature models. The underlying Eclipse enables us to implement the feature extraction and the questionnaire as a plugin.

@@

Contributions:
\begin{itemize}
\item Automatic feature model generation based on descriptive files and naming conventions as a foundation for the thereon based questionnaire.
\item Eclipse plugin, that enables the creation of a questionnaire based on a configuration file and the associated feature model. The liberties of the configuration file specification allows very personalized questionnaires.
\item The questionnaire changes as choices are made based on the logic behind the configuration file and the dependencies of the feature model. This enables a responsive questionnaire that prevents unnecessary questions.
\item Exiting the questionnaire always results in a valid configured variant to always ensure a valid configuration.
\end{itemize}
